---
title: "Requests on the web service"
author: "I.Sanchez & A. Charleroy (INRA MISTEA)"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    number_sections: yes
    toc: yes
vignette: >
  %\VignetteIndexEntry{Connection on the web service}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<!---
Program  : OpenSILEXrequests.Rmd
Author   : I.Sanchez (MISTEA), A.Charleroy (MISTEA)
Objective: a vignette for opensilexWSClientR library
           an introduction to requesting an OpenSILEX web service
Creation : 19/03/2018
Update   : 09/04/2021
-->

```{r,echo=TRUE,message=FALSE, warning=FALSE}
  library(opensilexWSClientR)
```

The **opensilexWSClientR** library allows an openSILEX user to create a connection to the web services of this system of information **openSILEX**. If the user wants to have access to openSILEX data for example, he has to load this library and create a connexion to the specified url.

# Creation of an identifier
Ask permission to request to a web service. The user has to give a identifier, a password and a web service URL:

```{r,echo=TRUE,message=FALSE, warning=FALSE}
  # If you want to access to an OpenSILEX web service, you have to insert the address of the WS and the port
  # connectToOpenSILEXWS(identifier="guest@opensilex.org",password="guest", url = "http://www.opensilex.org/rest/")
```

# Set log level
To get more or less informations on calls:

```{r,echo=TRUE,eval=FALSE,message=FALSE, warning=FALSE}
  setLogLevel("DEBUG")
```

```{r,echo=TRUE,message=FALSE, warning=FALSE}
  # If you want to access to a private web service, you have to insert the address of the WS and the port
  # connectToOpenSILEXWS(identifier="guest@opensilex.org",password="guest", url = "www.opensilex.org/rest/")
```

# Session info

```{r session,echo=FALSE,message=FALSE, warning=FALSE}
  sessionInfo()
```

# References
1. R Development Core Team (2015). R: A language and environment for statistical computing. R Foundation for
      Statistical Computing, Vienna, Austria. ISBN 3-900051-07-0, URL http://www.R-project.org.
